The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-05-12 albatros_paper.tex
HCC working on section 1

Very few experiments have measured the radio sky at $\lesssim 30$~MHz.
Comprehensive reviews exist elsewhere (\attention{find a good
  reference}), and here, we highlight only a few specific examples.
At the very lowest frequencies, the state of the art among
ground-based measurements dates from the 1950s, when Reber and Ellis
caught brief glimpses of the $2.1$~MHz sky at $\sim
5$\degree\ resolution, using an array of 192~dipoles~\citep{reber,
  article, 1988A&A...195..372W}.  A few space-based missions have also
performed measurements at similarly low frequency ranges; for example,
the Radio Astronomy Explorer-2 operated at \SIrange{0.025}{13}{\MHz}
with $\sim 10$\degree\ resolution at
\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
resolution finer than few-degree scales exist only at higher
frequencies.  For example, the Dominion Radio Astrophysical
Observatory surveyed the northern sky at \SI{22}{\MHz} with
\SIrange{1.1}{1.7}{\degree} resolution~\citep{1999A&AS..137....7R},
and most recently, the Owens Valley Long Wavelength Array mapped the
sky with \SI{15}{\arcminute} resolution between 36.528~MHz and
73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
list is not comprehensive, it does illustrate the dearth of
information about the $\lesssim 30$~MHz sky and the lack of high
resolution measurements at the lowest frequencies.

>>>>

Very few experiments have measured the radio sky at $\lesssim 30$~MHz;
here, we highlight only four specific examples.  At the very lowest
frequencies, the state of the art among ground-based measurements
dates from the 1950s, when Reber and Ellis caught brief glimpses of
the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an array of
192~dipoles~\citep{reber, article, 1988A&A...195..372W}.  A few
space-based missions have also performed measurements at similarly low
frequency ranges; for example, the Radio Astronomy Explorer-2 operated
at \SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
resolution finer than few-degree scales exist mainly at higher
frequencies.  For example, the Dominion Radio Astrophysical
Observatory surveyed the northern sky at \SI{22}{\MHz} with
\SIrange{1.1}{1.7}{\degree} resolution~\citep{1999A&AS..137....7R},
and most recently, the Owens Valley Long Wavelength Array mapped the
sky with \SI{15}{\arcminute} resolution between 36.528~MHz and
73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
list is not comprehensive, it does illustrate the dearth of
information about the $\lesssim 30$~MHz sky and the lack of high
resolution measurements at the lowest frequencies.  As a first step
toward laying the groundwork for possible future cosmological
measurements,...finish this sentence...
